High-Dim Project

### 2014-12-19 highdim-paper/paper.tex
Doc updated

\section{Introduction}
We motivate our project by considering the text classification problem: 
can we accurately classify text documents by topic. With the rapid growth 
of online information, text categorization has become one of the key techniques 
for handling and organizing text data. Text categorization techniques are used 
not only to filter spam emails, as we are mostly familiar, but also to classify 
news stories, to find interesting information on the WWW, and to guide a 
user's search through hypertext. Since building text classifiers by hand is 
difficult and time-consuming, it is advantageous to learn classifiers from examples. \\

@@

Given the co-occurence matrix $Z$, a simple greedy algorithm below is used to generates groups for the features.

\begin{algorithm}
  \For{$i \gets 0, \ldots, rows(Z) $}{
	   Get the indices of the N largest columns from row i\\
       Output these indices to a new group\\
       Mark all cell in these columns in the matrix Z to be 0.\\
  }
\end{algorithm}

Groups created from this method are more meaning semantically and more granular. Further granularty can be achieved by couting the frequency of two features in sentence level other than article level.\\

>>>>

\section{Introduction}
Our motivation for this project comes from text classification problem: 
can we accurately classify text documents by topics. With the rapid growth 
of online information, text categorization has become one of the key techniques 
for handling and organizing text data. Text categorization techniques are used 
not only to filter spam emails, as we are mostly familiar, but also to classify 
news stories, to find interesting information on the WWW, and to guide a 
user's search through hypertext. Since building text classifiers by hand is 
difficult and time-consuming, it is advantageous to learn classifiers from examples. \\

@@

Given the co-occurence matrix $Z$, a simple greedy algorithm below is used to generates groups for the features. The algorithm generates non-overlapping groups. To generate overlapping groups, skip step 3.

\begin{algorithm}
  \For{$i \gets 0, \ldots, rows(Z) $}{
	   1) Get the indices of the N largest columns from row i\\
       2) Output these indices to a new group\\
       3) Mark all cells in these columns in the matrix Z to be 0.\\
  }
\end{algorithm}

Groups created from this method are more meaningful semantically and more granular. Further granularty can be achieved by couting the frequency of two features in sentence level other than article level.\\
